Estimating Neighborhood Rents with Scraped Data

### 2018-06-03 dashboard/index.rmd
a little more progress on the project site

---
title: ""
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "hesscl.com", href: "http://hesscl.com", align: right}
       - {title: "Project Home", icon: "fa-home", href: "http://hesscl.com/smooth-sea/index.html", align: left} 
    orientation: columns
    theme: bootstrap
    logo: "../logo.svg"
    source_code: "https://github.com/hesscl/smooth-sea"
---

@@

Most graphics include some level of interactivity, usually either hover-over tooltip information or a slider to control various views of the graphic. Clicking on cases will highlight data elements in most graphics, and double-clicking will reset the graphic. You can download the source code and data for this project from Github [here](https://github.com/hesscl/smooth-sea).

Contact Chris Hess at [hesscl@uw.edu](mailto://hesscl@uw.edu) for more information about this research.

>>>>

---
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "hesscl.com", href: "http://hesscl.com", align: right}
       - {title: "Project Home", icon: "fa-home", href: "http://hesscl.com/smooth-sea/index.html", align: left} 
    orientation: columns
    theme: bootstrap
    logo: "../logo.svg"
    source_code: "https://github.com/hesscl/smooth-sea"
---

@@

Most graphics include some level of interactivity, usually either hover-over tooltip information or a slider to control various views of the graphic. Clicking on cases will highlight data elements in most graphics, and double-clicking will reset the graphic.

### 2018-06-03 index.rmd
fixing landing page + adding under construction notice
a little more progress on the project site

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess"
date: "June 2, 2018"
output: 
  html_document
---

<br>
<br>

## Project Contents

@@

## See also

@@

## Contact Informatiion

>>>>

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess"
output: 
  html_document:
      include:
        after_body: footer.html
---

This project is under construction and subject to change at any moment!

### Contents

@@

### See also

@@

### Contact

Email Chris Hess at [hesscl@uw.edu](mailto://hesscl@uw.edu) for more information about this research.

### 2018-06-03 manuscript/index.Rmd
a little more progress on the project site

Demand for rental housing units in Seattle, WA surged in the past decade, due to relative scarcity in available housing amidst a period of historic population growth. Growing shares of households are unable to buy a home short of "driving till they qualify", and among households who rent a substantial share pay 30%, if not more of their incomes on their housing costs. The rising cost of housing therefore has a direct role in neighborhood processes of "demographic inversion" like urban gentrification and suburbanizing poverty. Census data (i.e. decennial and American Community Survey) have common currency among scholars and practitioners interested in metropolitan housing markets, but neverthless possess a substantial limitation for research in tight housing markets like Seattle---that is, at least two years elapse between data collection and publication, if not more. This publication schedules prohibit analyzing any market dynamics beyond long-term trends, particularly among smaller areas of aggregation like neighborhoods. While more up-to-date options for neighborhood rent data exist through privately-held companies, such data can be somewhat of a black box in their creation and may be biased towards the costs of corporate-held properties. This would-be problem for academic researchers creates an opportunity for applying web scraping methods to generate a novel data on housing availability and costs.

@@

![Figure 1. Map of Seattle (left), Seattle Craigslist one-bedroom listing point and 2D-density map (right).](../output/map_point_density.png)
<br>

@@

![Figure 4. Scatter plot of neighborhood 1-bedroom rents across Craigslist and Dupre+Scott. Craigslist represents median asking rent among all one-bedroom listings, Dupre+Scott consists of median contract rents among one-bedroom units in 20+ unit properties.](../output/rent_scatter_across_1B.png)
<br>

>>>>

Demand for rental housing units in Seattle, WA surged in the past decade, due to relative scarcity in available housing amidst a period of historic population growth. Growing shares of households are unable to buy a home short of "driving till they qualify", and among households who rent a substantial share pay 30%, if not more of their incomes on their housing costs. The rising cost of housing therefore has a direct role in neighborhood processes of "demographic inversion" like urban gentrification and suburbanizing poverty. American Community Survey data have common currency among scholars and practitioners interested in metropolitan housing markets, but neverthless possess a substantial limitation for research in tight housing markets like Seattle---that is, at least two years elapse between data collection and publication, if not more. This publication lag for ACS data prohibits analyzing any market dynamics beyond long-term trends, particularly for estimates of smaller areas of aggregation like neighborhoods where ACS uses 5-year rolling-average methods as well. While more up-to-date options for neighborhood rent data exist through privately-held companies, such data can be somewhat of a black box in their creation and may be biased towards the costs of corporate-held properties. This would-be problem for academic researchers creates an opportunity for applying web scraping methods to generate a novel data on housing availability and costs.

@@

![Figure 1. Map of Seattle (left), Seattle Craigslist one-bedroom listing point and 2D-density map (right).](../output/map_point_density.png)

@@

![Figure 4. Scatter plot of neighborhood 1-bedroom rents across Craigslist and Dupre+Scott. Craigslist represents median asking rent among all one-bedroom listings, Dupre+Scott consists of median contract rents among one-bedroom units in 20+ unit properties.](../output/rent_scatter_across_1B.png)
